decompr: trade flow decomposition for Global Value Chain analysis

### 2014-12-18 README.Rmd
Update README.Rmd

---
title: "decompr: trade flow decomposition for Global Value Chain analysis"
author: "Bastiaan Quast and Victor K??mmritz"
date: "Wednesday, November 26, 2014"
output: md_document
bibliography: bibliography.bib
---

>>>>

---
title: "decompr: trade flow decomposition for Global Value Chain analysis"
author: "Bastiaan Quast and Victor Kummritz"
date: "Wednesday, November 26, 2014"
output: md_document
bibliography: bibliography.bib
---
